A Statistical Framework to Investigate the Optimality of Neural Networks for Linear Inverse Problems

### 2022-03-11 manuscript/main.tex
Added CIBM ack stuff

\author{Pakshal~Bohra, Pol del Aguila Pla, Jean-Fran\c{c}ois~Giovannelli and~Michael~Unser,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
\thanks{This work was funded by the Swiss National Science Foundation under Grant 200020\_184646 / 1.

P. Bohra and M. Unser are with the Biomedical Imaging Group, \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, 1015 Lausanne, Switzerland (e-mail: pakshal.bohra@epfl.ch; michael.unser@epfl.ch).

J.F. Giovannelli is with IMS (Univ. Bordeaux, CNRS, B-INP), UMR 5218, F-33400 Talence, France (e-mail: jean-francois.giovannelli@u-bordeaux.fr).
}

}% <-this % stops a space

@@

>>>>

\author{Pakshal~Bohra, Pol~{del Aguila Pla},~\IEEEmembership{Member,~IEEE},
Jean-Fran\c{c}ois~Giovannelli, and Michael~Unser,~\IEEEmembership{Fellow,~IEEE}
\thanks{This work was funded by the Swiss National Science Foundation under
Grant 200020\_184646 / 1.}
\thanks{P.~{del Aguila Pla} is with the CIBM Center for Biomedical Imaging,
Switzerland.}
\thanks{P. Bohra, P.~{del Aguila Pla} and M. Unser are with the Biomedical
Imaging Group, \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, 1015
Lausanne, Switzerland (e-mail: pakshal.bohra@epfl.ch;
pol.delaguilapla@eplf.ch; michael.unser@epfl.ch).}
\thanks{J.F. Giovannelli is with IMS (Univ. Bordeaux, CNRS, B-INP), UMR 5218,
F-33400 Talence, France (e-mail: jean-francois.giovannelli@u-bordeaux.fr).
}}%

@@

\section{Acknowledgements}

    \input{cibm_ack}
